Test-driven Knowledge Graph Construction

### 2023-05-06 doc/paper4.tex
Remove trailing spaces
Highlight that the combination and application is what is novel here

The following text describes the proposed method for knowledge graph construction and demonstrates its use to build a knowledge graph about antigen covid tests.

>>>>

In summary, the hereby described method borrows approaches either from ontology engineering or software development in general and proposes a novel way how to combine them for knowledge graph construction. The following text characterizes the method and demonstrates its use for building a knowledge graph about antigen covid tests.
